New approaches for boosting to uniformity

### 2014-10-07 assets/paperdraft/paper_draft.tex
Mike edits

\author{
Aleksandar Bukva$^e$, 
Vladimir Gligorov$^d$,
Alex Rogozhnikov$^{a,b}$\thanks{Corresponding author.}~,\newline
Andrey Ustyuzhanin$^{b,f,g}$ and
Mike Williams$^c$\\
\llap{$^a$}Lomonosov Moscow State University, Moscow, Russia\\
\llap{$^b$}Yandex, Moscow, Russia\\
\llap{$^c$}Massachusetts Institute of Technology, Cambridge, MA, United States \\
\llap{$^d$}Organisation Europ\'eenne pour la Recherche Nucl\'eaire (CERN), Geneva, Switzerland  \\
\llap{$^e$}Faculty of Physics, Belgrade, Serbia \\
\llap{$^f$}Moscow Institute of Physics and Technology, Moscow, Russia\\
\llap{$^g$}Imperial College, London, UK\\
E-mail: \email{alex.rogozhnikov@yandex.ru}}

@@

\section{Timings}

@@

%\textcolor{red}{xxx}

The link on the repository ans links to final notebooks with results in the article.

@@

These results were obtained using events generated with the official LHCb simulation, and we are grateful to the LHCb collaboration for this privilege. 
We particularly acknowledge the work of the LHCb Simulation and Core Computing teams in tuning the simulation software and managing the productions of simulated events.

@@

\bibitem{Sjostrand:2006za}
{"Sj\"{o}strand, Torbj\"{o}rn and Mrenna, Stephen and Skands, Peter"},
\emph{PYTHIA 6.4 physics and manual},
\href{http://dx.doi.org/10.1088/1126-6708/2006/05/026}
{\emph{JHEP} {\bf 05} (2006) 026}.
[\hepph{0603175}]

\bibitem{LHCb-PROC-2010-056}
{"Belyaev, I. and others"},
\emph{Handling of the generation of primary events in GAUSS, the LHCb simulation framework},
\href{http://dx.doi.org/10.1109/NSSMIC.2010.5873949}
{\emph{NSS/MIC} {\bf IEEE} (2010) 1155}.

\bibitem{Lange:2001uf}
{"Lange, D. J."},
\emph{The EvtGen particle decay simulation package},
\href{http://dx.doi.org/10.1016/S0168-9002(01)00089-4}
{\emph{NIM} {\bf A462} (2001) 152-155}.

\bibitem{Golonka:2005pn}
{"Golonka, Piotr and Was, Zbigniew"},
\emph{PHOTOS Monte Carlo: a precision tool for QED corrections in $Z$ and $W$ decays},
\href{http://dx.doi.org/10.1140/epjc/s2005-02396-4}
{\emph{EPJ} {\bf C45} (2006) 97-107}.
[\hepph{0506026}]

\bibitem{Allison:2006ve}
{"Allison, John and Amako, K. and Apostolakis, J. and Araujo, H. and Dubois, P.A. and others"},
\emph{Geant4 developments and applications},
\href{http://dx.doi.org/10.1109/TNS.2006.869826}
{\emph{IEEE TNS} {\bf 53} (2006) 270}.

\bibitem{Agostinelli:2002hh}
{"Agostinelli, S. and others"},
\emph{Geant4: a simulation toolkit},
\href{http://dx.doi.org/10.1016/S0168-9002(03)01368-8}
{\emph{NIM} {\bf A506} (2003) 250}.

\bibitem{LHCb-PROC-2011-006}
{"Clemencic, M and others"},
\emph{The LHCb simulation application, GAUSS : design, evolution and experience},
\href{http://dx.doi.org/10.1088/1742-6596/331/3/032023}
{\emph{J. Phys. Conf. Ser.} {\bf 331} (2011) 032023}.

@@

@@

\appendix
%\section{Uniformity Measurement}
\input{parts/metrics}
%\section{Approaches Proposed}
\input{parts/approaches}

>>>>

\author{
Alex Rogozhnikov$^{a,b}$\thanks{Corresponding author.}~,
Aleksandar Bukva$^c$, 
Vladimir Gligorov$^d$,
Andrey Ustyuzhanin$^{b,e,f}$ and
Mike Williams$^g$\\
\llap{$^a$}Lomonosov Moscow State University, Moscow, Russia\\
\llap{$^b$}Yandex, Moscow, Russia\\
\llap{$^c$}Faculty of Physics, Belgrade, Serbia \\
\llap{$^d$}Organisation Europ\'eenne pour la Recherche Nucl\'eaire (CERN), Geneva, Switzerland  \\
\llap{$^e$}Moscow Institute of Physics and Technology, Moscow, Russia\\
\llap{$^f$}Imperial College, London, UK\\
\llap{$^g$}Massachusetts Institute of Technology, Cambridge, MA, United States \\
E-mail: \email{alex.rogozhnikov@yandex.ru}}

@@

\section{CPU Resources}

@@

UPDATE THIS WITH CODE LOCATION.
%The link on the repository ans links to final notebooks with results in the article.

@@

These results were obtained using events generated with the official LHCb simulation, and we are grateful to the LHCb collaboration for this privilege. 
We particularly acknowledge the work of the LHCb Simulation and Core Computing teams in tuning the simulation software and managing the productions of simulated events.
MW is supported by NSF grant PHY-1306550.

@@

@@

\bibitem{Sjostrand:2006za}
T.~Sj\"{o}strand, S.~Mrenna and P.~Skands,
\emph{PYTHIA 6.4 physics and manual},
\href{http://dx.doi.org/10.1088/1126-6708/2006/05/026}
{\emph{JHEP} {\bf 05} (2006) 026}.
[\hepph{0603175}]

\bibitem{LHCb-PROC-2010-056}
I.~Belyaev, I. {\em et al.},
\emph{Handling of the generation of primary events in GAUSS, the LHCb simulation framework},
\href{http://dx.doi.org/10.1109/NSSMIC.2010.5873949}
{\emph{NSS/MIC} {\bf IEEE} (2010) 1155}.

\bibitem{Lange:2001uf}
D.J.~Lange,
\emph{The EvtGen particle decay simulation package},
\href{http://dx.doi.org/10.1016/S0168-9002(01)00089-4}
{\emph{NIM} {\bf A462} (2001) 152-155}.

\bibitem{Golonka:2005pn}
P.~Golonka and Z.~Was,
\emph{PHOTOS Monte Carlo: a precision tool for QED corrections in $Z$ and $W$ decays},
\href{http://dx.doi.org/10.1140/epjc/s2005-02396-4}
{\emph{EPJ} {\bf C45} (2006) 97-107}.
[\hepph{0506026}]

\bibitem{Allison:2006ve}
J.~Allison {\em et al.},
\emph{Geant4 developments and applications},
\href{http://dx.doi.org/10.1109/TNS.2006.869826}
{\emph{IEEE TNS} {\bf 53} (2006) 270}.

\bibitem{Agostinelli:2002hh}
S.~Agostinelli {\em et al.},
\emph{Geant4: a simulation toolkit},
\href{http://dx.doi.org/10.1016/S0168-9002(03)01368-8}
{\emph{NIM} {\bf A506} (2003) 250}.

\bibitem{LHCb-PROC-2011-006}
M~Clemencic {\em et al.},
\emph{The LHCb simulation application, GAUSS : design, evolution and experience},
\href{http://dx.doi.org/10.1088/1742-6596/331/3/032023}
{\emph{J. Phys. Conf. Ser.} {\bf 331} (2011) 032023}.

@@

\appendix
%\section{Uniformity Measurement}
\input{parts/metrics}
%\section{Approaches Proposed}
%\input{parts/approaches}

### 2014-10-07 assets/paperdraft/parts/dataset.tex
Mike edits

\begin{figure}[] 
  \centering 
  \includegraphics[width=0.49\textwidth]{DP_sig.pdf}
  \includegraphics[width=0.49\textwidth]{DP_bkgd.pdf}
  \caption{\label{fig:dalitz} Dalitz-plot distributions for (left) signal and (right) background for the $D_s^\pm\to\pi^+\pi^-\pi^\pm$.  The three pions are labeled here as 1, 2 and 3.}
\end{figure}

Figure~\ref{fig:dalitz} shows the Dalitz-plot distributions for signal and background events.  These samples are split into training and testing samples and then various BDTs are trained.  For the BDTs designed to produce uniform selections, the $\vec{y}$ variates are the Dalitz masses with the choice of uniform selection efficiency on signal candidates in the Dalitz-plot.  
Figure~\ref{fig:dalitz_rocs} shows the ROC curves obtained for the various classifiers studied in this paper.  For the UGBFL algorithms, there is a choice to be made for the value $\alpha$ which defines the relative weight of the flatness loss {\em vs} AdaLoss.  As expected, increasing $\alpha$, which increases the weight of AdaLoss, drives the ROC curve to be similar to AdaBoost.  Analysts will need to choose how much ROC performance to sacrifice to gain uniformity in the selection efficiency.  In general, the ROC curves for the uniform-driven BDTs are not too different from AdaBoost.

\begin{figure}[] 
  \centering 
  \includegraphics[width=0.49\textwidth]{ROC_DP.pdf}
  \includegraphics[width=0.49\textwidth]{ROC_DP_Alpha.pdf}
  \caption{\label{fig:dalitz_rocs} (left) ROC curves for classifier algorithms studied in this paper.  (right) ROC curves for UGBFL(bin) for differnet values of $\alpha$.}
\end{figure}

Figure~\ref{fig:dalitz_results} shows the efficiency obtained for each classifier {\em vs} distance from the a corner of the Dalitz-plot\footnote{The Dalitz-plot is essentially a triangle with three corners. Our defnition of this distance is ${\rm MIN}\left[(m(D_s)-m(\pi))^2 - m_{ij}^2\right]$, where $ij$ is 12, 13 and 23.}.  The AdaBoost algorithm, as expected, produces a much lower efficiency in the interesting corner regions.  The kNNAdaBoost algorithm does not improve upon the AdaBoost result much.  This is likely due to the fact that while kNNAdaBoost uses non-local kNN information, it does not utilize global information.
The UGBFL (binned and unbinned kNN) and uBoost algorithms each produce an efficiency which is statistically consistent with uniform across the Dalitz plot.  
As stated above, the analyst is free to optimize the choice of $\alpha$ for UGBFL by defining a metric that involves signal efficiency, background rejection and uniformity, {\em e.g.}, using uniformity metrics discussed in detail in Appendix~A.

\begin{figure}[] 
  \centering 
  \includegraphics[width=0.49\textwidth]{DP_compare.pdf}
  \caption{\label{fig:dalitz_results} Efficiency {\em vs} distance to a corner of the Dalitz-plot.  An arbitrary working point of 50\% integrated efficiency is displayed.}
\end{figure}

As a separate study using the same data samples, consider the case where one has simulated signal events and uses data from a {\em nearby} region, a so-called sideband, for background.  This is a common situation in particle-physics analyses.  Figure~\ref{fig:md_results} shows the training samples used.  A major problem can arise in these situations as typically input variates to the BDT are correlated with the parent particle mass.  Therefore, the BDT may learn to reject the background in the training using the fact that the mass of the background and signal candidates is different.  This is just an artifact of how the background sample is obtained and will not be true for background candidates {\em under} the signal peak.  Figure~\ref{fig:md_results} shows the background mis-indentifcation rate {\em vs} $D$ candidate mass.  AdaBoost has clearly learned to use this mis-match in signal and background candidate masses in the training.   The background in the region of the signal is about three times higher than one would expect from looking only at the sideband data.

@@

Figure~\ref{fig:md_results} also shows the background mis-indentifcation rate {\em vs} $D$ candidate mass for the various uniform classifiers where $y = m(D)$ and the choice is for uniformity in the background efficiency\footnote{The algorithms in this paper can easily be made uniform on signal, background or both.}.  
The uBoost algorithm does better than AdaBoost here but is still not optimal.  The way that uBoost achieves uniformity is not such that it can be trusted to work outside the region of training.  The algorithms presented in this paper each does well in achieving similar performance in the training and signal regions.  
Consider, {\em e.g.}, the UGBFL approach to achieving uniform selection efficiency.  In this case the training drives the BDT response itself to have the same PDF everywhere in the region $1.75 < m(D) < 1.85$~GeV (the training region).  
This does not gaurantee that the BDT response is truly independent of $m(D)$ outside the training region, but does strongly suppress learning to use $m(D)$ and in this example results in the desired behavior.  
Finally, if both high and low $m(D)$ sidebands had been used, it is possible for a BDT to create a fake peak near the signal peak location.  The use of UGBFL greatly reduces the chances and possible size of such an effect.

>>>>

\begin{figure}[] 
  \centering 
  \includegraphics[width=0.49\textwidth]{DP_sig.pdf}
  \includegraphics[width=0.49\textwidth]{DP_bkgd.pdf}
  \caption{\label{fig:dalitz} Dalitz-plot distributions for (left) signal and (right) background for the $D_s^\pm\to\pi^+\pi^-\pi^\pm$.  The three pions are labeled here as 1, 2 and 3 and ordered according to increases momentum.}
\end{figure}

Figure~\ref{fig:dalitz} shows the Dalitz-plot distributions for signal and background events.  These samples are split into training and testing samples and then various BDTs are trained.  For the BDTs designed to produce uniform selections, the $\vec{y}$ variates are the Dalitz masses with the choice of uniform selection efficiency on signal candidates in the Dalitz-plot.  
Figure~\ref{fig:dalitz_rocs} shows the ROC curves obtained for the various classifiers studied in this paper.  For the uGBFL algorithms, there is a choice to be made for the value $\alpha$ which defines the relative weight of the flatness loss {\em vs} AdaLoss.  As expected, increasing $\alpha$, which increases the weight of AdaLoss, drives the ROC curve to be similar to AdaBoost.  Analysts will need to choose how much ROC performance to sacrifice to gain uniformity in the selection efficiency.  In general, the ROC curves for the uniform-driven BDTs are not too different from AdaBoost.

\begin{figure}[] 
  \centering 
  \includegraphics[width=0.49\textwidth]{ROC_DP.pdf}
  \includegraphics[width=0.49\textwidth]{ROC_DP_Alpha.pdf}
  \caption{\label{fig:dalitz_rocs} (left) ROC curves for classifier algorithms studied in this paper.  For the uGBFL algorithms $\alpha=0.02$ is shown.  (right) ROC curves for uGBFL(bin) for differnet values of $\alpha$.}
\end{figure}

Figure~\ref{fig:dalitz_results} shows the efficiency obtained for each classifier {\em vs} distance from the a corner of the Dalitz-plot\footnote{The Dalitz-plot is essentially a triangle with three corners. Our defnition of this distance is ${\rm MIN}\left[(m(D_s)-m(\pi))^2 - m_{ij}^2\right]$, where $ij$ is 12, 13 and 23.}.  The AdaBoost algorithm, as expected, produces a much lower efficiency in the interesting corner regions.  The kNNAdaBoost algorithm does not improve upon the AdaBoost result much.  This is likely due to the fact that while kNNAdaBoost uses non-local kNN information, it does not utilize global information.  The uGBkNN algorithm overcompensates and drives the efficiency higher at the corners.  This suggests that if this algorithm is to be used some stopping criteria or {\em throttle} of the event-weighting updating should be implemented.  
The uGBFL (binned and unbinned kNN) and uBoost algorithms each produce an efficiency which is statistically consistent with uniform across the Dalitz plot.  
As stated above, the analyst is free to optimize the choice of $\alpha$ for uGBFL by defining a metric that involves signal efficiency, background rejection and uniformity, {\em e.g.}, using uniformity metrics discussed in detail in Appendix~A.

\begin{figure}[] 
  \centering 
  \includegraphics[width=0.49\textwidth]{DP_compare.pdf}
  \caption{\label{fig:dalitz_results} Efficiency {\em vs} distance to a corner of the Dalitz-plot.  An arbitrary working point of 50\% integrated efficiency is displayed. For the uGBFL algorithms $\alpha=0.02$ is shown.}
\end{figure}

As a separate study using the same data samples, consider the case where one has simulated signal events and uses data from a {\em nearby} region, a so-called sideband, for background.  This is a common situation in particle-physics analyses.  Figure~\ref{fig:md_results} shows the training samples used.  A major problem can arise in these situations as typically input variates to the BDT are correlated with the parent particle mass.  Therefore, the BDT may learn to reject the background in the training using the fact that the mass of the background and signal candidates is different.  This is just an artifact of how the background sample is obtained and will not be true for background candidates {\em under} the signal peak.  Figure~\ref{fig:md_results} shows the background mis-identification rate {\em vs} $D$ candidate mass.  AdaBoost has clearly learned to use this mis-match in signal and background candidate masses in the training.   The background in the region of the signal is about three times higher than one would expect from looking only at the sideband data.

@@

Figure~\ref{fig:md_results} also shows the background mis-identification rate {\em vs} $D$ candidate mass for the various uniform classifiers where $y = m(D)$ and the choice is for uniformity in the background efficiency\footnote{The algorithms in this paper can easily be made uniform on signal, background or both.}.  
The uBoost algorithm does better than AdaBoost here but is still not optimal.  The way that uBoost achieves uniformity is not such that it can be trusted to work outside the region of training.  The algorithms presented in this paper each does well in achieving similar performance in the training and signal regions.  
Consider, {\em e.g.}, the uGBFL approach to achieving uniform selection efficiency.  In this case the training drives the BDT response itself to have the same PDF everywhere in the region $1.75 < m(D) < 1.85$~GeV (the training region).  
This does not guarantee that the BDT response is truly independent of $m(D)$ outside the training region, but does strongly suppress learning to use $m(D)$ and in this example results in the desired behavior.  
Finally, if both high and low $m(D)$ sidebands had been used, it is possible for a BDT to create a fake peak near the signal peak location.  The use of uGBFL greatly reduces the chances and possible size of such an effect.

### 2014-10-07 assets/paperdraft/parts/metrics.tex
Mike edits

\subsection{Standard Deviation of Efficiency on Bins (SDE)}

@@

\subsection{Theil Index of Efficiency}
\def\theil{\text{Theil}}

@@

\subsection{Distribution Similarity Approach}
\label{sec:similarity}

@@

\subsection{Knn-based modifications}

@@

\subsection{Advantages and Disadvantages of Different Metrics}
\subsubsection{Theil and SDE}
Let us compare two metrics that have proven most appropriate for our problem, SDE and Theil. We have some masses distributed uniformly in $[0,1]$, some constant $\alpha$ from interval $[0,1]$. 
The predictions are correlated with mass via beta distribution.
First distribution with a peak is obtained by generating a prediction for each event according to its mass:
\[
	p_{\rm peak} \thicksim \text{Beta}(\alpha \mean{m}, \abs{m - \mean{m}})
\]
The second distribution is obtained by flipping:
\[
	p_{\rm pit} \thicksim 1 - \text{Beta}(\alpha \mean{m}, \abs{m - \mean{m}})
\]
SDE should show no changes if we flip the distribution, while the Theil should make difference between pit and peak.

@@

\subsubsection{$D \to hhh$}
When our classifiers where applied to data set $D \to hhh$ we got uniformity measures for the SDE and Theil
metrics shown in Fig.~\ref{fig:d2hhhsdetheil}.
\begin{figure}[h]
\centering
		% TODO use metrics on signal for signal, use metrics on bck for bck.
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/D23hSignalEffs.png}
			\caption{Metrics for $D \to hhh$ signal.}
		\end{subfigure}
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/D23hBgEffs.png}
			\caption{Metrics for $D \to hhh$ background.}
		\end{subfigure}
		\caption{Uniformity metrics for the $D \to hhh$ data set. The (top) signal and (bottom) background uniformities are plotted as a function of the training stage of a given classifier, listed in the legends on the leftmost plots. \label{fig:d2hhhsdetheil}}
\end{figure}

>>>>

\subsection*{Standard Deviation of Efficiency on Bins (SDE)}

@@

\subsection*{Theil Index of Efficiency}
\def\theil{\text{Theil}}

@@

\subsection*{Distribution Similarity Approach}
\label{sec:similarity}

@@

\subsection*{Knn-based modifications}

@@

\subsection*{Advantages and Disadvantages of Different Metrics}
\subsubsection*{Theil and SDE}
Let us compare two metrics that have proven most appropriate for our problem, SDE and Theil. We have some masses distributed uniformly in $[0,1]$, some constant $\alpha$ from interval $[0,1]$. 
The predictions are correlated with mass via beta distribution.
First distribution with a peak is obtained by generating a prediction for each event according to its mass:
\[
	p_{\rm peak} \thicksim \text{Beta}(\alpha \mean{m}, \abs{m - \mean{m}})
\]
The second distribution is obtained by flipping:
\[
	p_{\rm pit} \thicksim 1 - \text{Beta}(\alpha \mean{m}, \abs{m - \mean{m}})
\]
SDE should show no changes if we flip the distribution, while the Theil should make difference between pit and peak.

@@

\subsubsection*{$D \to hhh$}
When our classifiers where applied to data set $D \to hhh$ we got uniformity measures for the SDE and Theil
metrics shown in Fig.~\ref{fig:d2hhhsdetheil}.
\begin{figure}[h]
\centering
		% TODO use metrics on signal for signal, use metrics on bck for bck.
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/D23hSignalEffs.png}
			\caption{Metrics for $D \to hhh$ signal.}
		\end{subfigure}
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/D23hBgEffs.png}
			\caption{Metrics for $D \to hhh$ background.}
		\end{subfigure}
		\caption{Uniformity metrics for the $D \to hhh$ data set. The (top) signal and (bottom) background uniformities are plotted as a function of the training stage of a given classifier, listed in the legends on the leftmost plots. \label{fig:d2hhhsdetheil}}
\end{figure}

### 2014-10-07 assets/paperdraft/parts/timings.tex
Mike edits

One drawback of the uBoost technique is that it has a high degree of computational complexity: 
while AdaBoost trains $M$ trees (a user-defined number), uBoost builds $100 \times M$ trees.  
The algorithms presented in this paper only build $M$ trees; however, the boosting involves some more complicated algorithms.  Training each of the $M$ trees scales as follows for $N$ training events:
\begin{itemize}
       \item kNNAdaBoost: $O(k \times N)$;
	\item UGBkNNknn: $O(k \times N)$ for $A_{\rm knn}$, and  
	$O( \text{\#nonzero elements in the matrix})$ for arbitrary matrix $A$;
	\item UGBFL(bin): $O(N \ln N)$;
	\item UGBFL(kNN): $O(N \ln N + N k \ln k) $.
\end{itemize}
In the example analysis studied in this paper, we find that the training time for these new algorithms is within a factor of two the same as AdaBoost.  The CPU-resource usage of these new algorithms is not prohibative.

>>>>

One drawback of the uBoost technique is that it has a high degree of computational complexity: 
while AdaBoost trains $M$ trees (a user-defined number), uBoost builds $100 \times M$ trees.  
The algorithms presented in this paper only build $M$ trees; however, the boosting involves some more complicated algorithms.  Training each of the $M$ trees scales as follows for $N$ training events:
\begin{itemize}
       \item kNNAdaBoost: $O(k \times N)$;
	\item uGBkNNknn: $O(k \times N)$ for $A_{\rm knn}$, and  
	$O( \text{\#nonzero elements in the matrix})$ for arbitrary matrix $A$;
	\item uGBFL(bin): $O(N \ln N)$;
	\item uGBFL(kNN): $O(N \ln N + N k \ln k) $.
\end{itemize}
In the example analysis studied in this paper, we find that the training time for these new algorithms is within a factor of two the same as AdaBoost.  The CPU-resource usage of these new algorithms is not prohibitive.

### 2014-10-07 assets/paperdraft/tmp/paper_draft.tex
Mike edits

\author{
Alex Rogozhnikov$^{a,b}$\thanks{Corresponding author.}~,
Aleksandar Bukva$^c$, 
Vladimir Gligorov$^d$,
Andrey Ustyuzhanin$^{b,e,f}$ and
Mike Williams$^g$\\
\llap{$^a$}Lomonosov Moscow State University, Moscow, Russia\\
\llap{$^b$}Yandex, Moscow, Russia\\
\llap{$^c$}Faculty of Physics, Belgrade, Serbia \\
\llap{$^d$}Organisation Europ\'eenne pour la Recherche Nucl\'eaire (CERN), Geneva, Switzerland  \\
\llap{$^e$}Moscow Institute of Physics and Technology, Moscow, Russia\\
\llap{$^f$}Imperial College, London, UK\\
\llap{$^g$}Massachusetts Institute of Technology, Cambridge, MA, United States \\
E-mail: \email{alex.rogozhnikov@yandex.ru}}

@@

% AMS packages:

\usepackage{amsmath, amsthm, amsfonts, xspace}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}

@@

\def\x {\ensuremath{\vec{x}}\xspace}
\def\y {\ensuremath{\vec{y}}\xspace}
\def\knn{\text{knn}}
\def\knni{\text{knn}(i)}

@@

@@

\section{CPU Resources}

@@

UPDATE THIS WITH CODE LOCATION.
%The link on the repository ans links to final notebooks with results in the article.

@@

These results were obtained using events generated with the official LHCb simulation, and we are grateful to the LHCb collaboration for this privilege. 
We particularly acknowledge the work of the LHCb Simulation and Core Computing teams in tuning the simulation software and managing the productions of simulated events.
MW is supported by NSF grant PHY-1306550.

@@

\bibitem{ref:FS1997}
{Y. Freund, and R. Schapire},
\emph{A Decision-Theoretic Generalization of On-Line Learning and an Application to Boosting}, 
{\emph{Journal of Computer and System Sciences} {\bf 55(1)} (August 1997) 119-139}.

\bibitem{ref:uboost} 
J. Stevens and M. Williams,
{\em uBoost: A boosting method for producing uniform selection efficiencies from multivariate classifiers}, 
JINST {\bf 8}, P12013 (2013). 
[arXiv:1305.7248]

\bibitem{ref:F1999}
{Jerome H. Friedman},
\emph{Greedy Function Approximation: A Gradient Boosting Machine},
\href{http://statweb.stanford.edu/~jhf/ftp/trebst.pdf}
{\emph{Annals of Statistics} {\bf 29} (2000) 1189-1232}.

\bibitem{Sjostrand:2006za}
T.~Sj\"{o}strand, S.~Mrenna and P.~Skands,
\emph{PYTHIA 6.4 physics and manual},
\href{http://dx.doi.org/10.1088/1126-6708/2006/05/026}
{\emph{JHEP} {\bf 05} (2006) 026}.
[\hepph{0603175}]

\bibitem{LHCb-PROC-2010-056}
I.~Belyaev, I. {\em et al.},
\emph{Handling of the generation of primary events in GAUSS, the LHCb simulation framework},
\href{http://dx.doi.org/10.1109/NSSMIC.2010.5873949}
{\emph{NSS/MIC} {\bf IEEE} (2010) 1155}.

\bibitem{Lange:2001uf}
D.J.~Lange,
\emph{The EvtGen particle decay simulation package},
\href{http://dx.doi.org/10.1016/S0168-9002(01)00089-4}
{\emph{NIM} {\bf A462} (2001) 152-155}.

\bibitem{Golonka:2005pn}
P.~Golonka and Z.~Was,
\emph{PHOTOS Monte Carlo: a precision tool for QED corrections in $Z$ and $W$ decays},
\href{http://dx.doi.org/10.1140/epjc/s2005-02396-4}
{\emph{EPJ} {\bf C45} (2006) 97-107}.
[\hepph{0506026}]

\bibitem{Allison:2006ve}
J.~Allison {\em et al.},
\emph{Geant4 developments and applications},
\href{http://dx.doi.org/10.1109/TNS.2006.869826}
{\emph{IEEE TNS} {\bf 53} (2006) 270}.

\bibitem{Agostinelli:2002hh}
S.~Agostinelli {\em et al.},
\emph{Geant4: a simulation toolkit},
\href{http://dx.doi.org/10.1016/S0168-9002(03)01368-8}
{\emph{NIM} {\bf A506} (2003) 250}.

\bibitem{LHCb-PROC-2011-006}
M~Clemencic {\em et al.},
\emph{The LHCb simulation application, GAUSS : design, evolution and experience},
\href{http://dx.doi.org/10.1088/1742-6596/331/3/032023}
{\emph{J. Phys. Conf. Ser.} {\bf 331} (2011) 032023}.

% The examples of items:
% \bibitem{bib1}
% Authors,
% \emph{Title},
% \emph{J. Ref.} \textbf{vol} (year) page.

% \bibitem{bib2}
% A. Pietropaolo et al., \emph{DINS measurements on VESUVIO in the
%     resonance detector configuration: proton mean kinetic energy in
%     water}, \jinst{1}{2006}{P04001}.

% \bibitem{bib3}
% A.I. Harris,
% \emph{Spectroscopy with multichannel correlation radiometers},
% \href{http://dx.doi.org/10.1063/1.1898643}
% {\emph{Rev.\ Sci.\ Instrum.} {\bf 76} (2005) 054503}
% [\astroph{0504449}].

% \bibitem{bib4}
% G.F. Knoll, \emph{Radiation detection and measurements}, John Wiley
%     and Sons, Inc., New York 2000.

% \bibitem{bib5}
% V. Dangendorf, \emph{Time-resolved fast-neutron imaging with a
% pulse-counting image intensifier}, in proceedings of
% \emph{International workshop on fast neutron detectors and
% applications}, April, 3--6, 2006 University of Cape Town, South Africa
% \pos{PoS(FNDA2006)008}.

@@

\appendix
%\section{Uniformity Measurement}
\input{parts/metrics}
%\section{Approaches Proposed}
%\input{parts/approaches}

>>>>

\author{
Aleksandar Bukva$^{\rm ADD}$, 
Vladimir Gligorov$^d$,
Alex Rogozhnikov$^{a,b}$\thanks{Corresponding author.}~ ,
Andrey Ustuzhanin$^b$ and
Mike Williams$^c$\\
\llap{$^a$}Lomonosov Moscow State University, Moscow, Russia\\
\llap{$^b$}Yandex LLC, Moscow, Russia\\
\llap{$^c$}Massachusetts Institute of Technology, Cambridge, MA, United States \\
\llap{$^d$}Organisation Europ\'eenne pour la Recherche Nucl\'eaire (CERN), Geneva, Switzerland  \\
E-mail: \email{alex.rogozhnikov@yandex.ru}}

@@

% AMS packages:
\usepackage{amsmath, amsthm, amsfonts, xspace}

@@

\def \x {\ensuremath{\vec{x}}\xspace}
\def \y {\ensuremath{\vec{y}}\xspace}
\def\knn{\text{knn}}
\def\knni{\text{knn}(i)}

@@

%\section{Uniformity Measurement}
\input{parts/metrics}
%\section{Approaches Proposed}
\input{parts/approaches}

@@

\section{Timings}

@@

%\textcolor{red}{xxx}

The link on the repository ans links to final notebooks with results in the article.

@@

@@

\bibitem{ref:uboost} J. Stevens and M. Williams, {\em uBoost: A boosting method for producing uniform selection efficiencies from multivariate classifiers}, JINST {\bf 8}, P12013 (2013) [arXiv:1305.7248]

@@

\appendix
\section{Other Flatness Loss Criteria}

ADD THEIL, ETC DESCRIPTIONS AND HOW TO IMPLEMENT IN THE ALGORITHM HERE.
